Classification of short product Reviews using Semi-Supervised Learning

### 2012-09-03 docs/paper.tex
fixed capitalizations

   \begin{abstract}
      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy,and third annotated data is limited and costly to get.\\
      In this paper we address the problem of classifying short product reviews by using semisupervised learning. A Comparison among two semisupervised methods and a supervised method is given. Finally we propose different ways to improve the given results by injecting knowledge into the semisupervised models.
    \end{abstract}

@@

as prices of Smartphones became more accessible to people big communities

@@

In the Scenario of text classification Semi-supervised techniques present two advantages:\\

@@

Even though Classifying text has been a widely studied topic,the focus has been on long documents,

@@

This approach maps the data to a graph representation.
In this representation each Arc of the graph will connect two nodes only if the two nodes are similar,
the weights of the arcs are directly proportional to the similarity of the incident nodes.\\

@@

\subsection{Algorithm}
Let $Y_{ij}$ be the soft probability of labeling instance $i$ with label $j$.\\
\\
Given our semi-supervised task, then $Y$ can be divided into:\\
\\
$Y_{U}$:the soft labels for the unlabelled data\\
$Y_{L}$:the soft labels for the labelled data\\
\\
This means that $Y_{L}$ is given at the beginning of the problem
and the target is to find good values for $Y_{U}$.\\
\\
\textbf{Step 1 - Init}: In this step, the Labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
\\
\textbf{Step 2 - Propagation}: In this step, the Labels of neighbouring nodes are pushed.\\
Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
\begin{align}
Y^{t+1} = T Y^{t}
\end{align}
\\
\textbf{Step 3 - Clamp Labelled Data}: In this step, the Labels for $Y_{L}$ are clamped.\\
\\
\textbf{Step 4 - Repeat}: Repeat from step 2 until convergence.\\
\\
\textbf{Step 5 - Labeling Approach}: Once there is convergence, a label has to be chosen for each node in the graph, there is more than one approach.\\
The simplest approach would be to pick the label with the highest probability. \\
In ~\cite{Zhu:2005:SLG:1104523} there is an empirical analysis on more sophisticated approaches, there it is shown how this criteria can affect the performance, nevertheless for this experiment the simple approach was used.\\
\\
More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absorption algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
Nevertheless within this paper we call LP to the algorithm proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
\\
To summarize, in the experiment we convert our data into a complete graph,
each node is the feature vector of a comment, and the weight of each arc
corresponds to the similarity of the comments being incident to the arc.\\
This Graph is  fed to the Label Propagation Algorithm proposed by Zhu.\\

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabelled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
Learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
\\
For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
\\
By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.\\
With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
For the rest of the paper we will refer to this approach as Naive SL.

@@

For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\

@@

In overall the Naive SL could maintain the f-score given by the Supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\

@@

\item \textbf{Sparsity and Short Text}: feature vectors are very sparse and text is short. This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ''resolution", ''megapixels" and so on.\\
On the other hand in the short text classification, you got at most 144 characters per text, so you might end up only with a small subset of topic related words.
For example lets assume you have a set of good predictors in your labelled data and those predictors are the words: ''Camera" and ''resolution".If there is a comment saying just: ''it has a good amount of megapixels", it will be very unlikely to be classified correctly, unless there is another comment linking ''megapixels" with one of the predicting words in the seed set.\\
\\
With respect to the Topic Vocabulary, I would speculate that this really affect the performance. In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned. On top of that combine all the possible technical words that might appear with the labels $Camera$, $OS$, $Photography$.

>>>>

   \begin{abstract}
      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy,and third annotated data is limited and costly to get.\\
      In this paper we address the problem of classifying short product reviews by using semisupervised learning. A comparison among two semisupervised methods and a supervised method is given. Finally we propose different ways to improve the given results by injecting knowledge into the semisupervised models.
    \end{abstract}

@@

as prices of smartphones became more accessible to people big communities

@@

In the scenario of text classification Semi-supervised techniques present two advantages:\\

@@

Even though classifying text has been a widely studied topic,the focus has been on long documents,

@@

This approach maps the data to a graph representation.
In this representation each arc of the graph will connect two nodes only if the two nodes are similar,
the weights of the arcs are directly proportional to the similarity of the incident nodes.\\

@@

\subsection{Algorithm}
Let $Y_{ij}$ be the soft probability of labeling instance $i$ with label $j$.\\
\\
Given our semi-supervised task, then $Y$ can be divided into:\\
\\
$Y_{U}$:the soft labels for the unlabelled data\\
$Y_{L}$:the soft labels for the labelled data\\
\\
This means that $Y_{L}$ is given at the beginning of the problem
and the target is to find good values for $Y_{U}$.\\
\\
\textbf{Step 1 - Init}: In this step, the labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
\\
\textbf{Step 2 - Propagation}: In this step, the labels of neighbouring nodes are pushed.\\
Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
\begin{align}
Y^{t+1} = T Y^{t}
\end{align}
\\
\textbf{Step 3 - Clamp Labelled Data}: In this step, the Labels for $Y_{L}$ are clamped.\\
\\
\textbf{Step 4 - Repeat}: Repeat from step 2 until convergence.\\
\\
\textbf{Step 5 - Labeling Approach}: Once there is convergence, a label has to be chosen for each node in the graph, there is more than one approach.\\
The simplest approach would be to pick the label with the highest probability. \\
In ~\cite{Zhu:2005:SLG:1104523} there is an empirical analysis on more sophisticated approaches, there it is shown how this criteria can affect the performance, nevertheless for this experiment the simple approach was used.\\
\\
More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absorption algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
Nevertheless within this paper we call LP to the algorithm proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
\\
To summarize, in the experiment we convert our data into a complete graph,
each node is the feature vector of a comment, and the weight of each arc
corresponds to the similarity of the comments being incident to the arc.\\
This Graph is  fed to the Label Propagation Algorithm proposed by Zhu.\\

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabelled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the labelled Data.\\
By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
\\
For learning this tasks, first the words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
\\
By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.\\
With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
For the rest of the paper we will refer to this approach as Naive SL.

@@

For all the linear classifiers trained in the experiments a  Polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.\\

@@

In overall the Naive SL could maintain the f-score given by the supervised approach, in some cases was able to get a much better f-score by improving recall, in some other cases a slightly better recall resulted in a decline of the precision thus leading to a worse f-score.\\

@@

\item \textbf{Sparsity and Short Text}: feature vectors are very sparse and text is short. This could affect in the following ways, lets think again on the label $Camera$ for the Mobile  phone dataset, if we assume we are classifying long texts, an annotated instance can reveal a lot of the topic vocabulary , in this case words such as ''resolution", ''megapixels" and so on.\\
On the other hand in the short text classification, you got at most 144 characters per text, so you might end up only with a small subset of topic related words.
For example lets assume you have a set of good predictors in your labelled data and those predictors are the words: ''Camera" and ''resolution".If there is a comment saying just: ''it has a good amount of megapixels", it will be very unlikely to be classified correctly, unless there is another comment linking ''megapixels" with one of the predicting words in the seed set.\\
\\
With respect to the topic vocabulary, I would speculate that this really affect the performance. In the Hygienic Product and  Sportswear the term's range are more or less reduced, this is not the case of the mobile phone dataset, the range of topic vocabulary for each label is huge, just take into account the label $Application$, a comment can be given this label if it has a mention to a well known IOS or Android App, such as ''Angry Birds", furthermore take into account the label $Social$ $Network$ where social networks' names are mentioned. On top of that combine all the possible technical words that might appear with the labels $Camera$, $OS$, $Photography$.
